\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-27 papers/jss/article.Rnw
preferred options() specified at jstatsoft.org
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@858 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
Replace the second use of 'compare' in a sentence with another more specific and less duplicative word ('perform')
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@859 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% DE: I tend to have wider option(width=...) so this
%%     guarantees better line breaks
<<echo=FALSE,print=FALSE>>=
options(width=65, prompt="R> ", digits=4)
@

@@

Once the data serialization needs of an application become complex
enough, developers typically benefit from the use of an
\emph{interface description language}, or \emph{IDL}.  IDLs like
Protocol Buffers \citep{protobuf}, Apache Thrift, and Apache Avro
provide a compact well-documented schema for cross-language data
structures and efficient binary interchange formats.  Since the schema
is provided separately from the data, the data can be
efficiently encoded to minimize storage costs when
compared with simple ``schema-less'' binary interchange formats.
Many sources compare data serialization formats
and show Protocol Buffers compare very favorably to the alternatives; see
\citet{Sumaray:2012:CDS:2184751.2184810} for one such comparison.

>>>>

%% DE: I tend to have wider option(width=...) so this
%%     guarantees better line breaks
<<echo=FALSE,print=FALSE>>=
## cf http://www.jstatsoft.org/style#q12
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE, digits=4)
@

@@

Once the data serialization needs of an application become complex
enough, developers typically benefit from the use of an
\emph{interface description language}, or \emph{IDL}.  IDLs like
Protocol Buffers \citep{protobuf}, Apache Thrift, and Apache Avro
provide a compact well-documented schema for cross-language data
structures and efficient binary interchange formats.  Since the schema
is provided separately from the data, the data can be
efficiently encoded to minimize storage costs when
compared with simple ``schema-less'' binary interchange formats.
Many sources compare data serialization formats
and show Protocol Buffers perform favorably to the alternatives; see
\citet{Sumaray:2012:CDS:2184751.2184810} for one such comparison.
